Application

### 2021-10-28 main_application.Rmd
rewrite application

hod_ind_group <- data_hod %>% 
  left_join(cluster_result) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id, fill = group),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = group), size = 1) +
  facet_wrap(group~customer_id, 
             scales = "free_y",
              nrow=24) + 
  theme_application()+
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +    xlab("hour-of-day")  +
  scale_x_discrete(breaks = seq(0, 23, 3))
# + scale_y_continuous(breaks = NULL)

moy_ind_group <- data_moy %>% 
  left_join(cluster_result, by = c("customer_id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, 
                  group=customer_id, fill = group), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=customer_id, color = group), size = 1) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             nrow=24) +
    ylab("demand (in Kwh)") +
    xlab("month-of-year")  +
  theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7"))

wkndwday_ind_group <- data_wkndwday%>% 
  left_join(cluster_result, by = c("customer_id")) %>% 
  mutate(group  = as.factor(group)) %>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group), 
          #            color = as.factor(group)), k=5, alpha = 0.5) +
  geom_boxplot(aes(fill = group, color = group),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             nrow=24)  +
  theme_application()+
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7"))

@@

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=hour_day, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_grid(group~wknd_wday, 
             scales = "free_y", 
             labeller = "label_both") + 
  theme_bw() + theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +
  theme(legend.position = "bottom") 
```

>>>>

hod_ind_group <- data_hod %>% 
  left_join(cluster_result) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id, fill = group),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = group), size = 1) +
  facet_wrap(group~customer_id, 
             scales = "free_y",
              nrow=24) + 
  theme_application()+
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +    xlab("hour-of-day")  +
  scale_x_discrete(breaks = seq(0, 23, 3))+ theme(legend.position = "bottom")
# + scale_y_continuous(breaks = NULL)

moy_ind_group <- data_moy %>% 
  left_join(cluster_result, by = c("customer_id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, 
                  group=customer_id, fill = group), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=customer_id, color = group), size = 1) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             nrow=24) +
    ylab("demand (in Kwh)") +
    xlab("month-of-year")  +
  theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) + theme(legend.position = "bottom")

wkndwday_ind_group <- data_wkndwday%>% 
  left_join(cluster_result, by = c("customer_id")) %>% 
  mutate(group  = as.factor(group)) %>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group), 
          #            color = as.factor(group)), k=5, alpha = 0.5) +
  geom_boxplot(aes(fill = group, color = group),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             nrow=24)  +
  theme_application()+
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7"))  + theme(legend.position = "none")

@@

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=hour_day, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = group, color = group),alpha = 0.5)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_grid(group~wknd_wday, 
             scales = "free_y", 
             labeller = "label_both") + 
  theme_bw() + theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +
  theme(legend.position = "none") 
```
